\documentclass[a4paper,dvipdfmx,11pt,reqno]{amsart}
\usepackage{amsmath,amsthm,amssymb,mathrsfs,stmaryrd}
\usepackage{bm}
% \usepackage[bbgreekl]{mathbbol}
\usepackage{url}
\usepackage{color}
\usepackage{eucal}
\usepackage{slashed}
\usepackage{physics}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{tikz-3dplot}
\usetikzlibrary{intersections, calc, arrows, arrows.meta, shadows}
\usepackage[utf8]{inputenc} % for special characters
\usepackage[T1]{fontenc}
\usepackage[backend=biber,style=alphabetic,hyperref=true]{biblatex} % for bib-latex
\addbibresource{references_algebraic_k_theory.bib}
\usepackage{geometry} % margin settings
\geometry{margin=1.0in}
\usepackage{enumitem} % item style
\setlist[enumerate]{itemsep=2pt,parsep=2pt,before={\parskip=2pt}}
\setlist[description]{style=standard}
\usepackage[colorlinks=true,hyperindex, linkcolor=magenta, pagebackref=false, citecolor=cyan,pdfpagelabels]{hyperref} % link colors
\usepackage{cleveref}

\renewcommand{\baselinestretch}{1.1} % change the space between lines

\allowdisplaybreaks % allow page breaks in equations

% math definitions
\DeclareMathOperator{\Ob}{Ob}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Map}{Map}
\DeclareMathOperator{\Nat}{Nat}
\DeclareMathOperator{\myop}{op}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\fib}{fib}
\DeclareMathOperator{\cofib}{cofib}
\renewcommand{\mid}{\mathrm{mid}}
\DeclareMathOperator{\const}{const}
\DeclareMathOperator*{\colim}{colim}
\renewcommand{\ev}{\mathrm{ev}}
\DeclareMathOperator{\h}{h}
\DeclareMathOperator{\N}{N}
\DeclareMathOperator{\Fun}{Fun}

% categories (using mathcal)
\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\K}{\mathcal{K}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\W}{\mathcal{W}}
\renewcommand{\H}{\mathcal{H}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathcal{P}}
\renewcommand{\S}{\mathcal{S}}

% math definitions for K-theory
\DeclareMathOperator{\Seq}{Seq}
\DeclareMathOperator{\core}{core}
\DeclareMathOperator{\asscat}{asscat}
\DeclareMathOperator{\Span}{Span}
\DeclareMathOperator{\Idem}{Idem}
\DeclareMathOperator{\Ind}{Ind}
\DeclareMathOperator{\grp}{grp}
\DeclareMathOperator{\Calk}{Calk}
% \newcommand{\Ksp}{\mathcal{K}^{\mathrm{sp}}}

% categories (using math rm)
\newcommand{\An}{\mathrm{An}}
\newcommand{\Cat}{\mathrm{Cat}}
\newcommand{\Catlex}{\mathrm{Cat^{lex}}}
\newcommand{\Catperf}{\mathrm{Cat^{perf}}}
\newcommand{\Catst}{\mathrm{Cat^{st}}}
\newcommand{\Mon}{\mathrm{Mon}_{\mathbb{E}_{\infty}}}
\newcommand{\Grp}{\mathrm{Grp}_{\mathbb{E}_{\infty}}}
\newcommand{\Ar}{\mathrm{Ar}}
\newcommand{\TwAr}{\mathrm{TwAr}}
\newcommand{\Sp}{\mathrm{Sp}}
\newcommand{\sSet}{\mathrm{sSet}}

% math bb
\newcommand{\Einf}{\mathbb{E}_{\infty}}
\newcommand{\bbK}{\mathbb{K}}

% \code for prism
\usepackage{relsize}
\usepackage[bbgreekl]{mathbbol}
\usepackage{amsfonts}
\DeclareSymbolFontAlphabet{\mathbb}{AMSb} %to ensure that the meaning of \mathbb does not change
\DeclareSymbolFontAlphabet{\mathbbl}{bbold}
\newcommand{\prism}{{\mathlarger{\mathbbl{\Delta}}}}

% theorem style (using definition style)
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{definition*}{Definition}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{conjecture*}{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{example}[theorem]{Example}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{question}[theorem]{Question}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{newproof}[theorem]{Proof}

% ------------------------------------------------------

\begin{document}

\title{The Algebraic K-Theory of Stable \texorpdfstring{$\infty$}{infty}-Categories}
\author{Keima Akasaka}
\maketitle 

\begin{abstract}
  We summarize the algebraic K-theory of stable $\infty$-categories.
\end{abstract} 

% show depth in contents
\setcounter{tocdepth}{1}
\tableofcontents   


\section{Introduction}

This paper is a summary of the workshop on the algebraic K-theory held in Kyoto in September 2024.

\subsection{Notation}

From here all categories are assumed to be $\infty$-categories.
We let 
\begin{itemize}
  \item $\An$ denote the category of small anima.
  \item $\Cat$ denote the category of small categories.
  \item $\Catlex$ denote the category of small categories which admit finite limits, with left exact functors.
  \item $\Catst$ denote the category of small stable categories with exact functors.
  \item $\Catperf$ denote the category of small idempotent complete stable categories with exact functors.
  \item $\Sp$ denote the category of spectra.
\end{itemize}


\section{Preliminaries} \label{sec.preliminaries}

\subsection{The Grothendieck Group} 

In this section, we review the definition of the Grothendieck group for stable categories.

\begin{definition} \label{Ber.def.2.1}
  Let $(\C,\oplus)$ be a stable category, and let $X$ and $Y$ be objects of $\C$.
  We let $[X]$ denote the connected component of $X$.
  The connected component set $\pi_0(\core\C)$, together with the operation $+$ defined by 
  \begin{align*}
    [X] + [Y] := [X \oplus Y]
  \end{align*}
  form an ordinary monoid $(\pi_0(\core\C),+)$.
  We define the \textit{Grothendieck group} $\K_0(\C)$ of $\C$ as 
  \begin{align*}
    \K_0(\C) := (\pi_0(\core\C),+) / \sim,
  \end{align*}
  where $\sim$ is the equivalence relation generated by the following relation:
  $[X]=[X']+[X'']$ whenever $X' \to X \to X''$ is a cofiber sequence in $\C$.
\end{definition}

\begin{remark} \label{Ber.rem.2.2}
  Let $(\C,\oplus)$ be a stable category.
  Then the connected component set $\pi_0(\core\C)$ is the set of equivalence classes of objects of $\C$.
  Moreover, the Grothendieck group $\K_0(\C)$ is actually abelian.
  \begin{enumerate}
    \item The zero object $0$ of $\C$ defines a unit element $[0]$ in $\K_0(\C)$, since $X \to X \to 0$ is a cofiber sequence in $\C$ for every object $X$ of $\C$.
    \item For every object $X$ of $\C$, $[\Omega X]$ and $[\Sigma X]$ are inverse element of $[X]$ in $\K_0(\C)$, since $\Omega X \to 0 \to X$ and $X \to 0 \to \Sigma X$ are cofiber sequences in $\C$.
    \item For every objects $X$ and $Y$ of $\C$, we have $[X]+[Y]=[Y]+[X]$, since $X \to X \oplus Y \to Y$ and $Y \to X \oplus Y \to X$ are cofiber sequences in $\C$.
  \end{enumerate}
\end{remark}

\begin{remark}[Eilenberg swindle]
  Let $(\C,\oplus)$ be a stable category with countable coproducts.
  Then the Grothendieck group $\K_0(\C)$ is trivial.
  Indeed, for every object $X$ of $\C$, we have $[X] = 0$, since
  \begin{align*}
    X \to \bigoplus_{n \geq 0} X \to \bigoplus_{n \geq 1} X
  \end{align*}
  is a cofiber sequence in $\C$ and the last two terms are equivalent.
  It can be generalized to the algebraic K-theory (see \cref{Ber.prop.A.4}).
\end{remark}

\begin{remark} \label{Ber.rem.2.5}
  The construction $\C \mapsto \K_0(\C)$ determines a functor $\K_0 : \h\Catst \to \mathrm{Ab}$.
\end{remark}

\subsection{Arrow Categories and Twisted Arrow Categories} 

In this section, we recall the notions of (twisted) arrow categories.

\begin{definition}
  Let $\C$ be a category.
  We define the \textit{arrow category} $\Ar(\C)$ of $\C$ as 
  \begin{align*}
    \Ar(\C) := \Fun([1],\C).
  \end{align*} 
\end{definition}

\begin{definition} \label{Ber.rem.3.1}
  Let $\C$ be a category.
  The \textit{twisted arrow category} $\TwAr(\C)$ of $\C$ is the simplicial set defined by 
  \begin{align*}
    \TwAr(\C)_n := \Hom_{\mathrm{sSet}}([n] \star [n]^{\myop},\C)
  \end{align*}
  for every $n \geq 0$, where $\star$ denotes the join operator.
  By \cite[Proposition 5.2.1.3]{HA}, $\TwAr(\C)$ is a category.
\end{definition}

% \begin{definition}
%   Let $\C$ be a category.
%   We define the \textit{twisted arrow category} $\TwAr(\C)$ of $\C$ as a right fibration classifying the mapping anima functor.
%   That is, the source-target projection 
%   \begin{align*}
%     (s,t) : \TwAr(\C) \to \C \times \C^{\myop}
%   \end{align*}
%   is the right fibration classifying the mapping anima functor $\Map_{\C} : \C \times \C^{\myop} \to \An^{\myop}$.
% \end{definition}

\begin{remark} \label{Ber.rem.3.2}
  Let $\C$ be a category.
  We can describe objects and morphisms of $\Ar(\C)$ and $\TwAr(\C)$.
  \begin{itemize}
    \item The objects of both are morphisms in $\C$.
    \item A morphism from $f$ to $g$ in $\Ar(\C)$ is a diagram, depicted as 
    \[\begin{tikzpicture}[auto]
      \node (0) at (0,0) {$0$};
      \node (1) at (1.6,-0.6) {$0'$};
      \node (2) at (2.6,0.6) {$1.$};
      \node (3) at (1,1.8) {$1'$};
      \draw[->] (0) -- node[swap] {$f$} (1);
      \draw[->] (0) -- node {} (2);
      \draw[->] (0) -- node {} (3);
      \draw[->] (1) -- node {} (2);
      \draw[-, line width=6pt,draw=white] (1) -- node {} (3);
      \draw[->] (1) -- node {} (3);
      \draw[->] (2) -- node[swap] {$g$} (3);
    \end{tikzpicture}\]
    \item A morphism from $f$ to $g$ in $\TwAr(\C)$ is a diagram, depicted as 
    \[\begin{tikzpicture}[auto]
      \node (0) at (0,0) {$0$};
      \node (1) at (1.6,-0.6) {$0'$};
      \node (2) at (2.6,0.6) {$1.$};
      \node (3) at (1,1.8) {$1'$};
      \draw[->] (0) -- node[swap] {$f$} (1);
      \draw[->] (0) -- node {} (2);
      \draw[->] (0) -- node {} (3);
      \draw[->] (1) -- node {} (2);
      \draw[-, line width=6pt,draw=white] (1) -- node {} (3);
      \draw[->] (3) -- node {} (1);
      \draw[->] (2) -- node[swap] {$g$} (3);
    \end{tikzpicture}\]
  \end{itemize}
\end{remark}

\begin{notation} \label{Ber.p49}
  Let $\C$ be a stable category.
  We let $\Seq(\C)$ denote the full subcategory of $\Fun(\Delta^1 \times \Delta^1,\C)$ spanned by the bifiber sequences in $\C$.
\end{notation}

\begin{remark}
  Let $\C$ be a stable category.
  Then we have an equivalence of categories $\Seq(\C) \simeq \Ar(\C)$, which implies that the category $\Seq(\C)$ is stable.
\end{remark}

\begin{notation}
  Let $\C$ be a stable category.
  We define functors from $\Seq(\C)$ to $\C$ as follows:
  \begin{align*}
    \fib   : \Seq(\C) \to \C &: (X \to Y \to Z) \mapsto X, \\
    \mid   : \Seq(\C) \to \C &: (X \to Y \to Z) \mapsto Y, \\
    \cofib : \Seq(\C) \to \C &: (X \to Y \to Z) \mapsto Z.
  \end{align*}
\end{notation}


\section{Localization Properties of Functors} \label{sec.localization_properties}

In this section, we define various functors with localization properties: 
additive, Verdier-localizing, Karoubi-localizing, and grouplike functors.

We follow the terminology of \cite{CDH23}.
In \cite{CDH23}, these notions are defined for Poincar\'{e}-Verdier squares. 
We use the same terminology for Verdier squares.

\subsection{Verdier Sequences and Squares}

In this section, we recall the notions of (split) Verdier sequences and Karoubi sequences and there relative versions: (split) Verdier squares and Karoubi squares.

\begin{definition} \label{CDH23.rem.A.1.2}
  Let $\C \xrightarrow{f} \D \xrightarrow{p} \E$ be a sequence in $\Catst$.
  We will say that the sequence \textit{has vanishing composition} if the composition $pf$ is a zero object of $\Catst$.
  
  In this case, the composition $pf$ is equivalent to the functor $\C \to 0 \to \E$, since the full subcategory of $\Fun^{\mathrm{ex}}(\C,\E)$ spanned by the zero objects is contractible.
  That is, there exists the following commutative diagram:
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$\C$}; 
    \node (tr) at (1.5,1.5) {$\D$};
    \node (bl) at (0,0) {$0$}; 
    \node (br) at (1.5,0) {$\E.$}; 
    % horizontal lines
    \draw (tl) -- node {$f$} (tr); 
    \draw (bl) -- node[swap] {} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tr) -- node {$p$} (br); 
  \end{tikzpicture}\]
  We will say that the sequence is a \textit{fiber} (resp. \textit{cofiber}) sequence if the above diagram is a cartesian (resp. cocartesian) diagram.
\end{definition}

\begin{definition}[\cite{CDH23} Definition A.1.1] \label{CDH23.def.A.1.1}
  Let $\C \xrightarrow{f} \D \xrightarrow{p} \E$ be a sequence in $\Catst$ with vanishing composition.
  We will say that it is \textit{Verdier} if it is a bifiber sequence in $\Catst$.
  In this case, we will refer to the functor $f$ as the \textit{Verdier inclusion} and to the functor $p$ as the \textit{Verdier projection}.
\end{definition}

\begin{definition}[\cite{CDH23} Definition A.2.4] \label{CDH23.def.A.2.4}
  Let $\C \xrightarrow{f} \D \xrightarrow{p} \E$ be a Verdier sequence.
  We will say that it is \textit{split} if the functor $p$ admits both adjoint functors.
  In this case, we will refer to the functor $f$ as the \textit{split Verdier inclusion} and to the functor $p$ as the \textit{split Verdier projection}.
\end{definition}

\begin{definition}[\cite{CDH23} Definition A.3.5] \label{CDH23.def.A.3.5}
  Let $\C \xrightarrow{f} \D \xrightarrow{p} \E$ be a sequence in $\Catst$ with vanishing composition.
  We will say that it is \textit{Karoubi} if its idempotent completion $\C^{\natural} \to \D^{\natural} \to \E^{\natural}$ is a bifiber sequence in $\Catperf$.
  In this case, we will refer to the functor $f$ as the \textit{Karoubi inclusion} and to the functor $p$ as the \textit{Karoubi projection}.
\end{definition}

We can characterize Verdier inclusions and projections (\cref{CDH23.cor.A.1.10}).
The fiber of an exact functor $f : \C \to \D$ can be computed by its kernel $\ker(f)$.
On the other hand, its cofiber is described by the Verdier quotient.

\begin{definition}[\cite{CDH23} Definition A.1.3] \label{CDH23.def.A.1.3}
  Let $f : \C \to \D$ be an exact functor between stable categories.
  We will say that a morphism in $\D$ is an \textit{equivalence modulo} $\C$ in $\D$ if its fiber (or equivalently, its cofiber) belongs in the essential image of $f$.

  We define the category $\D/\C$ as the localization of $\D$ with respect to the set of equivalences modulo $\C$ in $\D$.
  We will refer to the category $\D/\C$ as the \textit{Verdier quotient} of $\D$ by $\C$.
\end{definition}

The next proposition implies that the Verdier quotient is universal.

\begin{proposition}[\cite{NS18} Theorem.1.3.3] \label{NS18.thrm.1.3.3}
  Let $f : \C \to \D$ be an exact functor between stable categories.
  Then
  \begin{enumerate}
    \item The Verdier quotient $\D/\C$ is stable, and the localization functor $\D \to \D/\C$ is exact.
    \item For every stable category $\E$, the restriction functor
    \begin{align*}
      \Fun^{\mathrm{ex}}(\D/\C,\E) \to \Fun^{\mathrm{ex}}(\D,\E)
    \end{align*}
    is fully faithful, and its essential image consists of the functors which vanish after composing with $f$.
    \item The sequence $\C \to \D \to \D/\C$ is a cofiber sequence in $\Catst$.
  \end{enumerate} 
\end{proposition}

\begin{proposition}[\cite{CDH23} Corollary A.1.10] \label{CDH23.cor.A.1.10}
  Let $\C \xrightarrow{f} \D \xrightarrow{p} \E$ be a sequence in $\Catst$ with vanishing composition.
  The following conditions are equivalent:
  \begin{enumerate}
    \item The sequence is Verdier.
    \item The functor $f$ is fully faithful and its essential image is closed under retracts in $\D$, and the functor $p$ exhibits $\E$ as the Verdier quotient of $\D$ by $\C$.
    \item The functor $f$ exhibits $\C$ as the kernel of $p$, and the functor $p$ is a localization.
  \end{enumerate}
\end{proposition}

We can characterize split Verdier inclusions and projections.

\begin{proposition}[\cite{CDH23} Corollary A.2.6] \label{CDH23.cor.A.2.6}
  Let $\C \xrightarrow{f} \D \xrightarrow{p} \E$ be a sequence in $\Catst$ with vanishing composition.
  The following conditions are equivalent:
  \begin{enumerate}
    \item The sequence is split Verdier.
    \item The functor $p$ admits fully faithful both adjoint functors.
    \item The functor $f$ is fully faithful and admits both adjoint functors.
  \end{enumerate}
\end{proposition}

We can characterize Karoubi inclusions and projections.

\begin{proposition}[\cite{CDH23} Corollary A.3.8] \label{CDH23.cor.A.3.8}
  Let $\C \xrightarrow{f} \D \xrightarrow{p} \E$ be a sequence in $\Catst$ with vanishing composition.
  The following conditions are equivalent:
  \begin{enumerate}
    \item The sequence is Karoubi.
    \item The functor $f$ is fully faithful and the functor $p$ has the dense essential image $p(\D) \subseteq \E$, and the induced functor $\D \to p(\D)$ is a Verdier projection.
  \end{enumerate}
\end{proposition}

We can describe Karoubi sequences using Ind-categories. 

\begin{theorem}[Thomason-Neeman's localization theorem] \label{Ber.thrm.3.47}
  Let $\C \xrightarrow{f} \D \xrightarrow{p} \E$ be a sequence in $\Catst$ with vanishing composition.
  The following conditions are equivalent:
  \begin{enumerate}
    \item The sequence is Karoubi.
    \item The sequence $\Ind(\C) \to \Ind(\D) \to \Ind(\E)$ is Verdier (of non-necessarily small categories).
  \end{enumerate}
\end{theorem}

We next introduce the relative versions of these sequences.

\begin{definition}[\cite{CDH23} Definition.1.5.1] \label{CDH23.def.1.5.1}
  A square in $\Catst$ is called
  \begin{itemize}
    \item \textit{Verdier} if it is cartesian and its both vertical maps are Verdier projections.
    \item \textit{split Verdier} if it is cartesian and its both vertical maps are split Verdier projections.
    \item \textit{Karoubi} if it is cartesian after idempotent completion and its both vertical maps are Karoubi projections.
  \end{itemize}
\end{definition}

\begin{remark} \label{Ber.rem.3.53}
  In \cref{CDH23.def.1.5.1}, the condition that the square is cartesian can be replaced by the condition that it is cocartesian.
  (See \cref{proof_of_Ber.rem.3.53}.)
\end{remark}

% \begin{remark} % p52
%   Every Verdier square is a Karoubi square, since the idempotent completion preserves small limits.
%   A Karoubi square is a Verdier square if and only if its both vertical maps are essentially surjective.
% \end{remark}

\subsection{Additive and Grouplike Functors}

In this section, we define additive, Verdier-localizing, Karoubi-localizing, and grouplike functors. 

\begin{definition}
  Let $\E$ be a category with a terminal object, and let $F : \Catst \to \E$ be a functor.
  We will say that $F$ is \textit{reduced} if $F(0)$ is equivalent to a terminal object of $\E$, where $0$ is a zero object in $\Catst$.
\end{definition}

\begin{definition}[\cite{HLS23} Definition 2.1] \label{HLS23.def.2.1} %\label{CDH23.def.1.5.4}
  Let $\E$ be a category with finite limits, and let $F : \Catst \to \E$ be a reduced functor.
  The functor $F$ is called 
  \begin{itemize}
    \item \textit{Verdier-localizing} if it takes every Verdier square in $\Catst$ to a cartesian square in $\E$.
    \item \textit{additive} if it takes every split Verdier square in $\Catst$ to a cartesian square in $\E$.
    \item \textit{Karoubi-localizing} if it takes every Karoubi square in $\Catst$ to a cartesian square in $\E$.
  \end{itemize}
\end{definition}

Every additive (resp. Verdier-localizing, Karoubi-localizing) functor $F : \Catst \to \E$ sends split Verdier sequences (resp. Verdier sequences, Karoubi sequences) to fiber sequences in $\E$.
If $\E$ is stable, the converse holds.

\begin{proposition}[\cite{CDH23} Proposition 1.5.5] \label{CDH23.prop.1.5.5}
  Let $\E$ be a category with finite limits, and let $F : \Catst \to \E$ be a reduced functor.
  If $\E$ is stable, then the following conditions are equivalent:
  \begin{enumerate}
    \item The functor $F$ is additive (resp. Verdier-localizing, Karoubi-localizing).
    \item The functor $F$ takes every split Verdier sequence (resp. Verdier sequence, Karoubi sequence) in $\Catst$ to a fiber sequence in $\E$.
    (See \cref{proof_of_CDH23.prop.1.5.5}.)
  \end{enumerate}
\end{proposition}

\begin{definition}[\cite{HLS23} Definition 2.1] %[\cite{CDH23} Definition 1.5.8] \label{CDH23.def.1.5.8}
  Let $\E$ be a category with finite limits, and let $F : \Catst \to \E$ be an additive functor.
  We will say that $F$ is \textit{grouplike} if it lifts to the category $\Mon(\E)$ takes values in the full subcategory $\Grp(\E)$ of $\Mon(\E)$.
\end{definition}

\begin{example}[\cite{CDH23} Example 1.5.10] \label{CDH23.eg.1.5.10}
  We give some (counter)examples.
  \begin{enumerate}
    \item The core functor $\core : \Catst \to \An$ is additive, but not grouplike. % since it preserves all limits.
    % \item The algebraic K-theory $\K : \Catst \to \An$ and the algebraic K-theory spectrum $\K_{\geq 0} : \Catst \to \Sp_{\geq 0}$ are Verdier-localizing (\cref{thrm.localization_theorem}) and grouplike (\cref{HLS23.cor.4.2}), but not Karoubi-localizing.
    \item The algebraic K-theory $\K : \Catst \to \An$ is Verdier-localizing (\cref{thrm.localization_theorem}) and grouplike (\cref{HLS23.cor.4.2}), but not Karoubi-localizing.
    \item The non-connective K-theory spectrum $\bbK : \Catst \to \Sp$ is Karoubi-localizing. 
    \item The functor $\K \circ (-)^{\natural} : \Catst \to \An$ is Karoubi-localizing (\cref{Ber.cor.5.52}), thus is Verdier-localizing (\cref{HLS23.obs.2.12}).
    % \item The functor $\K_{\geq 0} \circ (-)^{\natural} : \Catst \to \Sp$ is additive, but not Verdier-localizing.
  \end{enumerate}
\end{example}

\begin{proposition}[\cite{HLS23} Observation 2.2] \label{HLS23.obs.2.2} % also Ber.lem.3.75
  The additive, Verdier-localizing, Karoubi-localizing functors preserve finite products.
  (See \cref{proof_of_HLS23.obs.2.2}.)
\end{proposition}

\begin{proposition} \label{Ber.rem.3.65}
  Let $F : \Catst \to \E$ be an additive functor.
  If $\E$ is additive (TBA), then $F$ is grouplike.
\end{proposition}

\subsection{Additive Grouplike vs. Extension-splitting}

We can characterize additive grouplike functors by extension-splitting functors.
We will use \cref{HLS23.lem.2.5,HLS23.prop.2.4} to show that the algebraic K-theory is additive grouplike (\cref{HLS23.cor.4.2}).

\begin{definition}
  Let $\E$ be a category with finite limits, and let $F : \Catst \to \E$ be a reduced functor.
  We will say that $F$ is \textit{extension-splitting} if, for every stable category $\C$, the fiber-cofiber map
  \begin{align*}
    (\fib,\cofib) : \Seq(\C) \to \C^2
  \end{align*}
  induces an equivalence $F(\Seq(\C)) \to F(\C)^2$.
\end{definition}

We show that additive grouplike functors and extension-splitting functors are equivalent (\cref{HLS23.prop.2.4}). 

\begin{lemma}[\cite{HLS23} Lemma 2.5] \label{HLS23.lem.2.5}
  Let $\E$ be a category with finite limits, and let $F : \Catst \to \E$ be a reduced and product-preserving functor.
  The following conditions are equivalent:
  \begin{enumerate}
    \item The functor $F$ is extension-splitting.
    \item The functor $F$ sends the source-target projection $(s,t) : \Ar(\C) \to \C^2$ for every object stable category $\C$ to an equivalence in $\E$.
  \end{enumerate}
\end{lemma}

\begin{proposition}[\cite{HLS23} Proposition 2.4] \label{HLS23.prop.2.4}
  Let $\E$ be a category with finite limits, and let $F : \Catst \to \E$ be a reduced functor.
  The following conditions are equivalent:
  \begin{enumerate}
    \item The functor $F$ is additive grouplike.
    \item The functor $F$ is extension-splitting.
  \end{enumerate}
\end{proposition}

\subsection{Additive vs. Verdier-localizing}

In this section, we recall Waldhausen's fibration theorem.
We will use this theorem in the proof of the localization theorem (\cref{thrm.localization_theorem}).

\begin{notation}
  Let $\D$ be a stable category, let $\C$ be a stable full subcategory of $\D$, and let $\I$ be a category.
  We let $\Fun^{\C}(\I,\D)$ denote the full subcategory of $\Fun(\I,\D)$ spanned by the functors which take every map in $\I$ to an equivalence modulo $\C$.
\end{notation}

\begin{theorem}[Waldhausen's fibration theorem] \label{thrm.Waldhausen_fibration_theorem}
  Let $\C \to \D \to \E$ be a Verdier sequence, and let $F : \Catst \to \An$ be an additive grouplike functor.
  Then, for every $n \geq 0$, the constant map 
  \begin{align*}
    \const : \D \to \Fun^{\C}([n],\D) : X \mapsto (X \to \cdots \to X)
  \end{align*}
  induces a bifiber sequence of $\Einf$-groups 
  \begin{align*}
    F(\C) \to F(\D) \to |F\Fun^{\C}([-],\D)|.
  \end{align*}
\end{theorem}

We can deduce when an additive functor becomes a Verdier-localizing functor.

\begin{corollary}[\cite{HLS23} Corollary 2.10] \label{HLS23.cor.2.10}
  Let $F : \Catst \to \An$ be an additive functor.
  These conditions are equivalent:
  \begin{enumerate}
    \item The functor $F$ is Verdier-localizing.
    \item For every Verdier sequence $\C \to \D \to \E$, the canonical map $|F\Fun^{\C}([-],\D)| \to F(\E)$ is an equivalence of anima.
  \end{enumerate}
\end{corollary}

\subsection{Verdier-localizing vs. Karoubi-localizing}

The relationship between Verdier-localizing and Karoubi-localizing functors is as follows.

\begin{definition}
  Let $f : \C \to \D$ be a functor between categories.
  We will say that $f$ \textit{has the dense image} if, for every object $X$ of $\D$, there exists an object $Y$ in the essential image of $\C$ such that $Y$ is a retract of $X$. 
\end{definition}

\begin{definition}
  Let $f : \C \to \D$ be an exact functor between stable categories.
  We will say that $f$ is a \textit{Karoubi equivalence} if it is fully faithful and has the dense image.
\end{definition}

\begin{proposition}[\cite{HLS23} Observation 2.12] \label{HLS23.obs.2.12}
  Let $\E$ be a category with finite limits, and let $F : \Catst \to \E$ be a reduced functor.
  The following conditions are equivalent:
  \begin{enumerate}
    \item The functor $F$ is Karoubi-localizing.
    \item The functor $F$ is Verdier-localizing and inverts Karoubi equivalences.
  \end{enumerate}
\end{proposition}

We can construct Karoubi-localization functors from Verdier-localizing functors using the idempotent completion.

\begin{proposition}[\cite{HLS23} Lemma 2.13] \label{HLS23.lem.2.13}
  Let $\E$ be a category with finite limits, and let $F : \Catst \to \E$ be a Verdier-localizing functor.
  Suppose that $F$ takes every cartesian square in $\Catst$ whose vertical maps are dense inclusions, to a cartesian square in $\E$. 
  Then the functor $F \circ (-)^{\natural} : \Catst \to \E$ is Karoubi-localizing.
\end{proposition}


\section{The Algebraic K-Theory of Stable \texorpdfstring{$\infty$}{infty}-Categories} \label{sec.algebraic_k_theory}

In this section, we recall the Q-construction and define the algebraic K-theory. 
Furthermore, we introduce the S-construction and demonstrate that the definitions of the algebraic K-theory given by these two constructions are equivalent.

\subsection{Simplicial Objects}

In this section, we recall the basic notions of simplicial objects.

\begin{definition}
  The inclusion $\N(\prism) \subseteq \Cat$ induces an adjunction 
  \begin{align*}
    \asscat : \Fun(\N(\prism)^{\myop},\An) \rightleftarrows \Cat : \N^r.
  \end{align*}
  We will refer to the left adjoint as the \textit{associated category functor}, and to the right adjoint as the \textit{Rezk nerve}.
  % \[\begin{tikzpicture}[auto]
  %   \node (tl) at (0,1.5) {$\Fun(\N(\prism)^{\myop},\An)$};
  %   \node (bl) at (0,0) {$\N(\prism)$};
  %   \node (br) at (1.5,0) {$\Cat$};
  %   \draw[right hook->] (bl) -- node {} (br);
  %   \draw[->] (bl) -- node {$j$} (tl);
  %   \draw[bend left=40,->] (tl) -- node {$\asscat$} (br);
  %   \draw[bend left=40,->] (br) -- node {$\N^r$} (tl);
  % \end{tikzpicture}\]
\end{definition}

\begin{definition}
  Let $\C$ be a category.
  We will refer to a functor 
  \begin{align*}
    X : \N(\prism)^{\myop} \to \C
  \end{align*}
  as a \textit{simplicial object} of $\C$.
  We will say that $X$ is a \textit{simplicial anima} if $\C$ is $\An$.
\end{definition}

\begin{remark}
  Let $\C$ be a category.
  For every $n \geq 0$, we have an equivalence of anima
  \begin{align*}
    \N^r_n(\C) \simeq \Map_{\Cat}([n],\C) \simeq \core\Fun([n],\C).
  \end{align*}
\end{remark}

\begin{notation}
  We let $[n]$ denote the category the ordinary nerve $\N([n])$, instead of $\Delta^n$.
  On the other hand, we let $\Delta^n$ denote the functor 
  \begin{align*}
    \Delta^n := \Map_{\Cat}(-,[n]) : \N(\prism)^{\myop} \to \An.
  \end{align*}
  Then we have an equivalence of simplicial anima $\N^r([n]) \simeq \Delta^n$.
  % \begin{align*}
  %   \N^r([n])_m
  %   \simeq \Map_{\Cat}([m],[n])
  %   \simeq \core\Fun([m],[n])
  %   \simeq \Delta^n_m.
  % \end{align*}
\end{notation}

We define the Segal condition and completeness specifically for simplicial anima, although these concepts are applicable to every category.

\begin{definition}
  Let $X : \N(\prism)^{\myop} \to \An$ be a simplicial anima.
  We will say that $X$ is \textit{Segal} if the $n$-spine inclusion $\mathrm{sp}^n \subseteq \Delta^n$ induces an equivalence of anima 
  \begin{align*}
    X_n \simeq \Map_{\Fun(\N(\prism)^{\myop},\An)}(\Delta^n,X) \to \Map_{\Fun(\N(\prism)^{\myop},\An)}(\mathrm{sp}^n,X) \simeq X_1 \times_{X_0} \cdots \times_{X_0} X_1
  \end{align*}
  for every $n \geq 0$.
\end{definition}

The Segal condition can be interpreted as stating that a Segal simplicial anima has a unique spine lifting up to a choice of contractible spaces.

\begin{definition}
  Let $X : \N(\prism)^{\myop} \to \An$ be a Segal simplicial anima.
  We will say that $X$ is \textit{complete} if the following diagram is a cartesian diagram in $\An$.
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$X_0$}; 
    \node (tr) at (4,1.5) {$X_0 \times X_0$};
    \node (bl) at (0,0) {$X_3$}; 
    \node (br) at (4,0) {$X_1 \times X_1$}; 
    % horizontal lines
    \draw (tl) -- node {$\mathrm{diag}$} (tr); 
    \draw (bl) -- node[swap] {$(d^{\{0,2\}},d^{\{1,3\}})$} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tr) -- node {$(s,s)$} (br); 
    % pullback symbol (\lrcorner) in the lower right corner of (tl)
    \node at ([xshift=0.2cm, yshift=-0.2cm] tl.south east) {$\lrcorner$};
  \end{tikzpicture}\]
\end{definition}

The completeness condition can be understood as indicating that the higher simplices of a complete Segal simplicial anima correspond to equivalences related to its degenerate edges.

\begin{proposition}
  The Rezk nerve $\N^r : \Cat \to \Fun(\N(\prism)^{\myop},\An)$ is fully faithful.
  Moreover, its essential image precisely consists of complete Segal simplicial anima.
\end{proposition}

\subsection{The Algebraic K-Theory}

\begin{definition}[\cite{HLS23} Definition 3.1] \label{HLS23.def.3.1}
  Let $\C$ be a category with finite limits.
  For every $n \geq 0$, we let $Q_{n}(\C)$ denote the full subcategory of $\Fun(\TwAr[n],\C)$ spanned by the diagrams which take every square in $\TwAr[n]$ to a cartesian square in $\C$.

  The construction $n \mapsto Q_{n}(\C)$ determines a functor 
  \begin{align*}
    Q(\C) : \N(\prism)^{\myop} \to \Catlex
  \end{align*}
  and furthermore, the construction $\C \mapsto Q(\C)$ defines a functor 
  \begin{align*}
    Q : \Catlex \to \Fun(\N(\prism)^{\myop},\Catlex).
  \end{align*}
  We will refer to this functor as the \textit{(Quillen's) Q-construction}.
\end{definition}

\begin{proposition}[\cite{HLS23} Proposition 3.2] \label{HLS23.prop.3.2}
  Let $\C$ be a category with finite limits.
  Then the simplicial object in $\Catlex$
  \begin{align*}
    Q(\C) : \N(\prism)^{\myop} \to \Catlex
  \end{align*}
  is complete Segal.
  In particular, the simplicial anima 
  \begin{align*}
    \core Q(\C) : \N(\prism)^{\myop} \to \An
  \end{align*}
  is complete Segal.
  (See \cref{proof_of_HLS23.prop.3.2}.)
\end{proposition}

\begin{remark} \label{Ber.rem.4.32}
  \Cref{Ber.cor.4.31} implies that, if $\C$ is stable, so is $Q_n(\C)$.
  Therefore we obtain functors
  \begin{align*}
    Q(\C) : \N(\prism)^{\myop} \to \Catst 
    \quad \text{ and } \quad 
    Q : \Catst \to \Fun(\N(\prism)^{\myop},\Catst).
  \end{align*}
  Moreover, for every stable category $\C$, the category $Q(\C)$ is a complete Segal simplicial object in $\Catst$, since $\Catst$ is stable under finite limits in $\Cat$.
\end{remark}

\begin{definition}[\cite{HLS23} Definition 3.3] \label{HLS23.def.3.3}
  Let $\C$ be a category with finite limits.
  Then we define the \textit{category of spans} in $\C$ as 
  \begin{align*}
    \Span(\C) := \asscat \core Q(\C).
  \end{align*}
  The construction $\C \mapsto \Span(\C)$ determines a functor 
  \begin{align*}
    \Span : \Catlex \to \Cat.
  \end{align*}
\end{definition}

\begin{definition}[\cite{HLS23} Definition 3.4] \label{HLS23.def.3.4}
  Let $\C$ be a stable category.
  Then we define the \textit{algebraic K-anima} (or \textit{algebraic K-theory anima}, or \textit{projective class anima}) as 
  \begin{align*}
    \K(\C) := \Omega|\Span(\C)| \simeq \Omega|\core Q(\C)|
  \end{align*}
  where the base object of the loop space is given by the zero object of $\Span(\C)$.

  The construction $\C \mapsto \K(\C)$ determines a functor 
  \begin{align*}
    \K : \Catst \to \An. 
  \end{align*}
  We will refer to this functor as the \textit{algebraic K-theory} (or \textit{algebraic K-functor}).
\end{definition}

\begin{definition}
  Let $\C$ be a stable category.
  For every $n \geq 0$, we define the \textit{$n$-th K-group} of $\C$ as 
  \begin{align*}
    \K_n(\C) := \pi_n\K(\C).
  \end{align*}
\end{definition}

\begin{proposition}
  Let $\C$ be a stable category.
  Then we have an isomorphism of groups
  \begin{align*}
    \pi_0\K(\C) \simeq \K_0(\C),
  \end{align*}
  where $\K_0(\C)$ is the Grothendieck group of $\C$ (see \cref{Ber.def.2.1}).
\end{proposition}

\subsection{Waldhausen's S-Construction}

In this section, we construct the algebraic K-theory using Waldhausen's S-construction. 

\begin{definition}
  Let $\C$ be a stable category.
  An \textit{$[n]$-gapped object} of $\C$ is a functor $F : \Ar[n] \to \C$ which satisfies the following conditions:
  \begin{enumerate}
    \item For every $0 \leq i \leq n$, $F(i,i)$ is a zero object of $\C$.
    \item For every $i \leq j \leq k$, the following diagram is a (co)cartesian diagram in $\C$.
    \[\begin{tikzpicture}[auto,->] 
      \node (tl) at (0,1.5) {$F(i,j)$}; 
      \node (tr) at (2.5,1.5) {$F(i,k)$};
      \node (bl) at (0,0) {$0 \simeq F(j,j)$}; 
      \node (br) at (2.5,0) {$F(j,k)$}; 
      % horizontal lines
      \draw (tl) -- node {} (tr); 
      \draw (bl) -- node[swap] {} (br); 
      % vertical lines
      \draw (tl) -- node[swap] {} (bl);
      \draw (tr) -- node {} (br); 
      % pushout symbol (\ulcorner) in the upper left corner of (br)
      \node at ([xshift=-1.5cm, yshift=0.8cm] br.south east) {$\ulcorner$};
    \end{tikzpicture}\]
  \end{enumerate}
  We let $S_n(\C)$ denote the full subcategory of $\Fun(\Ar[n],\C)$ spanned by the $[n]$-gapped objects of $\C$.
\end{definition}

\begin{remark} \label{Ber.eg.4.1}
  Let $\C$ be a stable category.
  We can describe the low-dimensional simplices of $S_n(\C)$.
  \begin{itemize}
    \item The category $S_0(\C)$ is the full subcategory of $\C$ spanned by the zero objects of $\C$. 
    Thus $S_0(\C)$ is contractible.
    \item The category $S_1(\C)$ is equivalent to $\C$, since every object of $S_1(\C)$ is of the form $0 \to X \to 0$, where $X$ is an object of $\C$.
    \item The category $S_2(\C)$ is equivalent to the arrow category $\Ar(\C)$ of $\C$, since every object of $S_2(\C)$ is of the form $0 \to X' \to X \to X'' \to 0$, where $X' \to X \to X''$ is a cofiber sequence in $\C$. 
  \end{itemize}
\end{remark}

\begin{remark} \label{Ber.rem.4.2}
  Let $\C$ be a stable category.
  We have an equivalence of categories 
  \begin{align*}
    S_n(\C) \simeq \Fun([n-1],\C)
  \end{align*}
  for every $n \geq 0$.
  Thus, if $\C$ is stable, so is $S_n(\C)$.
\end{remark}

\begin{definition} \label{Ber.rem.4.5}
  The construction $n \mapsto S_n(\C)$ determines a functor 
  \begin{align*}
    S(\C) : \N(\prism)^{\myop} \to \Catst
  \end{align*}
  and furthermore, the construction $\C \mapsto S(\C)$ defines a functor 
  \begin{align*}
    S : \Catst \to \Fun(\N(\prism)^{\myop},\Catst).
  \end{align*}
  We will refer to this functor as \textit{(Waldhausen's) S-construction}.
\end{definition}

\begin{definition} \label{Ber.def.4.8}
  Let $\C$ be a stable category.
  Then we define the \textit{algebraic K-anima} as 
  \begin{align*}
    \K_S(\C) := \Omega|\core S(\C)|.
  \end{align*}
  The construction $\C \mapsto \K_S(\C)$ determines a functor 
  \begin{align*}
    \K_S : \Catst \to \An.
  \end{align*}
  We will refer to this functor as the \textit{algebraic K-theory}.
\end{definition}
 
\begin{remark} % p82
  Let $\C$ be a stable category.
  Then the anima $|\core S(\C)|$ admits the canonical base point given by the map 
  \begin{align*}
    0 \simeq \core S_0(\C) \to |\core S(\C)|.
  \end{align*}
  Moreover, $|\core S(\C)|$ is connected, since the canonical map 
  \begin{align*}
    0 \simeq \pi_0 \core S_0(\C) \to \pi_0 |\core S(\C)|
  \end{align*}
  is surjective.
\end{remark}

\begin{proposition} \label{Ber.prop.4.37}
  For every stable category $\C$, two definitions of algebraic K-anima (\cref{HLS23.def.3.4,Ber.def.4.8}) induce an equivalence of anima
  \begin{align*}
    \K(\C) \simeq \K_S(\C).
  \end{align*}
\end{proposition}

\newpage


\section{The Additivity Theorem}

The goal of this section is to prove the additivity theorem.

\begin{theorem}[\cite{HLS23} Theorem 4.1: The Additivity Theorem] \label{thrm.additivity_theorem}
  Let $\C$ be a stable category.
  Then the source-target projection induces an equivalence of anima 
  \begin{align*}
    |\Span(s,t)| : |\Span(\Ar(\C))| \to |\Span(\C)|^2.
  \end{align*}
\end{theorem}

Before proving \cref{thrm.additivity_theorem}, we show some corollaries.

\begin{corollary}[\cite{HLS23} Corollary 4.2] \label{HLS23.cor.4.2}
  The algebraic K-theory $\K : \Catst \to \An$ is additive grouplike.
\end{corollary}

\begin{proof}
  By \cref{HLS23.prop.2.4}, it suffices to show that $\K$ is a reduced functor and it is extension splitting.
  We have 
  \begin{align*}
    \K(0) \simeq \Omega|\Span(0)| \simeq \Omega|\core Q(0)| \simeq 0.
  \end{align*}
  The algebraic K-theory $\K$ preserves finite products.
  Then by \cref{HLS23.lem.2.5}, it is enough to show that $\K$ sends the source-target projection $(s,t) : \Ar(\C) \to \C^2$ to an equivalence of anima.
  That is, there is an equivalence $\K(s,t) : \K(\Ar(\C)) \to \K(\C)^2$.
  
  By \cref{thrm.additivity_theorem}, we have an equivalence $|\Span(\Ar(\C))| \to |\Span(\C)|^2$.
  Since the loop functor $\Omega$ preserves limits, we obtain an equivalence
  \begin{align*}
    \K(s,t) : \K(\Ar(\C)) \to \K(\C)^2.
  \end{align*}
\end{proof}

\begin{corollary}[Eilenberg swindle] \label{Ber.prop.A.4}
  Let $\C$ be a stable category with countable coproducts.
  Then the algebraic K-theory anima vanishes.
  That is, we have an equivalence of anima
  \begin{align*}
    \K(\C) \simeq 0.
  \end{align*}
\end{corollary}

\begin{proof}
  We first prove the following proposition:
  Let $\C$ and $\D$ be stable categories, and let $F' \to F \to F''$ be a cofiber sequence of exact functors from $\C$ to $\D$.
  Then we have 
  \begin{align*}
    \K(F) = \K(F') + \K(F'').
  \end{align*}
  Consider the following functors 
  \begin{align*}
    \mid, \fib+\cofib : \Seq(\Fun^{\mathrm{ex}}(\C,\D)) \to \Fun^{\mathrm{ex}}(\C,\D).
  \end{align*}
  Since $\K$ is extension-splitting (see \cref{HLS23.prop.2.4}), by Waldhausen's Additivity Theorem (TBA), we have an equivalence % Ber.lem.3.77
  \begin{align*}
    \K(\mid) \simeq \K(\fib) + \K(\cofib).
  \end{align*}
  We obtain the assertion by applying this proposition to the cofiber sequence $F' \to F \to F''$.

  Consider the following exact functor
  \begin{align*}
    F : \C \to \C : X \mapsto \bigoplus_{n \in \mathbb{N}} X_n .
  \end{align*}
  Then there exists a cofiber sequence 
  \begin{align*}
    \id_{\C} \to F \to F
  \end{align*}
  of exact functors on $\C$.
  By the above proposition, we have an equivalence 
  \begin{align*}
    \K(F) \simeq \K(\id_{\C}) + \K(\F). 
  \end{align*}
  Thus we have $\K(\id_{\C}) \simeq 0$ and, in particular $\K(\C) \simeq 0$.
\end{proof}

The proof of \cref{thrm.additivity_theorem} follows from the next two propositions.

\begin{proposition}[\cite{HLS23} Proposition 4.3] \label{HLS23.prop.4.3}
  Let $\C$ be a stable category.
  Then there are canonical equivalences of categories
  \begin{align*}
    \Span(\C) \to \Span(\C^{\myop}) 
    \quad \text{ and } \quad 
    \Span(\Ar(\C)) \simeq \Span(\TwAr(\C)).
  \end{align*}
  Moreover, they fit together into a natural commutative diagram 
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$\Span(\Ar(\C))$}; 
    \node (tr) at (5,1.5) {$\Span(\TwAr(\C))$};
    \node (bl) at (0,0) {$\Span(\C) \times \Span(\C)$}; 
    \node (br) at (5,0) {$\Span(\C) \times \Span(\C^{\myop}).$}; 
    \draw (tl) -- node {$\simeq$} (tr); 
    \draw (bl) -- node[swap] {$\simeq$} (br); 
    \draw (tl) -- node[swap] {$\Span(s,t)$} (bl);
    \draw (tr) -- node {$\Span(s,t)$} (br); 
  \end{tikzpicture}\]
\end{proposition}

\begin{proposition}[\cite{HLS23} Proposition 4.4] \label{HLS23.prop.4.4}
  Let $\C$ be a stable category.
  Then the source-target projection 
  \begin{align*}
    \Span(s,t) : \Span(\TwAr(\C)) \to \Span(\C) \times \Span(\C^{\myop})
  \end{align*}
  is cofinal.
\end{proposition}


\section{The Localization Theorem}

The goal of this section is to prove the localization theorem.

\begin{theorem}[\cite{HLS23} Theorem 6.1: The Localization Theorem] \label{thrm.localization_theorem}
  The algebraic K-theory $\K : \Catst \to \An$ is Verdier-localizing.
  % The algebraic K-theory $\K : \Catst \to \An$ and the algebraic K-theory spectrum $\K_{\geq 0} : \Catst \to \Sp$ are Verdier-localizing.
\end{theorem}

\begin{remark}
  By \cref{HLS23.cor.2.10}, an additive grouplike functor $F : \Catst \to \An$ is Verdier-localizing if and only if it satisfies the following condition:
  \begin{itemize}
    \item[$(\ast)$] For every Verdier sequence $\C \to \D \to \E$, the canonical map $|F\Fun^{\C}([-],\D)| \to F(\E)$ is an equivalence of anima.
  \end{itemize}
\end{remark}

The next proposition implies that it is enough to prove that the core functor satisfies $(\ast)$.

\begin{proposition}[\cite{HLS23} Proposition 6.2] \label{HLS23.prop.6.2} 
  Let $F : \Catst \to \An$ be an additive functor.
  If $F$ satisfies $(\ast)$, then $|FQ(-)|$ and $\Omega|FQ(-)|$ also satisfy $(\ast)$.
\end{proposition}

\begin{remark}
  If the core functor satisfies $(\ast)$, then the algebraic K-theory also satisfies $(\ast)$ since $\K(-) \simeq \Omega|\core Q(-)|$.
  % \begin{align*}
  %   \K(-) 
  %   \simeq \Omega|\Span(-)| 
  %   \simeq \Omega|\asscat\core Q(-)| 
  %   \simeq \Omega|\core Q(-)|.
  % \end{align*}
\end{remark}

% To prove \cref{HLS23.prop.6.2}, we need the following lemma.

% \begin{lemma}[\cite{HLS23} Lemma 6.4] \label{HLS23.lem.6.4} 
%   Verdier sequences are stable under applying the functor 
%   \begin{align*}
%     \Fun(\I,-) : \Catst \to \Catst
%   \end{align*}
%   for every finite poset $\I$.
% \end{lemma}

% From the above discussion, we need to show that the core functor satisfies $(\ast)$.

\begin{notation}
  Let $\D$ be a stable category, and let $\C$ be a stable subcategory of $\D$.
  We let $\D_{\C}$ denote the full subcategory of $\D$ spanned by the equivalences modulo $\C$ in $\D$.
\end{notation}

\begin{remark}
  Let $\D$ be a stable category, and let $\C$ be a stable subcategory of $\D$.
  We obtain an equivalence of anima 
  \begin{align*}
    \core\Fun^{\C}([-],\D) 
    \simeq \core\Fun([-],\D_{\C})
    \simeq \Map_{\Cat}([-],\D_{\C})
    \simeq \N^r(\D_{\C}).
  \end{align*}
  Then we have an equivalence 
  \begin{align*}
    |\core\Fun^{\C}([-],\D)| \simeq |\D_{\C}|,
  \end{align*}
  since the canonical map $|\N^r(\D_{\C})| \to |\D_{\C}|$ is an equivalence
\end{remark}

Thus it suffices to show the following proposition.

\begin{proposition}[\cite{HLS23} Proposition 6.6] \label{HLS23.prop.6.6} 
  Let $\D$ be a stable category, and let $\C$ be a stable subcategory of $\D$.
  Then the map 
  \begin{align*}
    |\D_{\C}| \to \core(\D/\C)
  \end{align*}
  is faithful.
  If the inclusion $\C \subseteq \D$ is a Verdier inclusion, then the above map is an equivalence.
\end{proposition}

\Cref{HLS23.prop.6.6} is a special case of the following proposition.

\begin{proposition}[\cite{HLS23} Proposition 6.8] \label{HLS23.prop.6.8} 
  Let $\C$ be a category, and let $S$ be a subcategory of $\C$.
  If $S$ is closed under 2-out-of-3 and pushouts in $\C$, then the map 
  \begin{align*}
    |S| = S[S^{-1}] \to \C
  \end{align*}
  is faithful. 
  Moreover, the following conditions are equivalent:
  \begin{enumerate}
    \item The inclusion $|S| \subseteq \core\C[S^{-1}]$ is fully faithful.
    \item The category $S$ is closed under 2-out-of-6 in $\C$.
    \item A morphism in $\D$ belongs to $S$ if and only if its source and target are in $S$ and it is invertible in $\C[S^{-1}]$.
  \end{enumerate}
\end{proposition}


\section{The Universality Theorem}

The goal of this section is to prove the universality theorem.

\begin{theorem}[\cite{HLS23} Theorem 5.1: The Universality Theorem] \label{thrm.universality_theorem}
  The algebraic K-theory $\K : \Catst \to \An$ is an initial additive grouplike functor under the core functor $\core : \Catst \to \An$.
  That is, the natural map $\tau : \core \Rightarrow \K$ is an initial object in $\Fun(\Catst,\An)^{\mathrm{add,grp}}_{\core/}$.
\end{theorem}

\begin{notation}
  Let $F : \Catst \to \An$ be a reduced functor.
  We denote a functor 
  \begin{align*}
    GF(-) := \Omega|FQ(-)| : \Catst \to \An. 
  \end{align*}
\end{notation}

\begin{example}
  the functor $G\core$ is equivalent to the algebraic K-theory $\K : \Catst \to \An$.
\end{example}

\begin{proof}[Proof of \cref{thrm.universality_theorem}]
  We want to show that the natural transformation $\tau : \core \Rightarrow \K$ induces an equivalence
  \begin{align*}
    \tau^{\ast} : \Nat(\K,F) \to \Nat(\core,F)
  \end{align*}
  for every additive grouplike functor $F : \Catst \to \An$.
  
  Now consider the following diagram 
  \[\begin{tikzpicture}[auto,->]
    \node (tl) at (0,4) {$\Nat(G\core,F)$};
    \node (tr) at (5,4) {$\Nat(\core,F)$};
    \node (ml) at (0,2) {$\Nat(GG\core,GF)$};
    \node (mr) at (5,2) {$\Nat(G\core,GF)$};
    \node (bl) at (0,0) {$\Nat(G\core,GF)$};
    \node (br) at (5,0) {$\Nat(\core,GF).$};
    % horizontal lines
    \draw (tl) -- node {$(\eta_{\core})^\ast$} (tr);
    \draw[red] (ml) -- node {$(G\eta_{\core})^\ast$} (mr);
    \draw (bl) -- node {$(\eta_{\core})^\ast$} (br);
    % vertical lines
    \draw (tl) -- node {$G$} (ml);
    \draw[red] (ml) -- node {$(\eta_{G\core})^\ast$} (bl);
    \draw (tr) -- node[swap] {$G$} (mr);
    \draw (mr) -- node[swap] {$(\eta_{\core})^\ast$} (br); 
    % bending lines 
    \draw[bend right=70,red] (tl) to node[swap] {$(\eta_{F})^\ast$} (bl);
    \draw[bend left=70,red] (tr) to node {$(\eta_{F})^\ast$} (br);
  \end{tikzpicture}\]
  The upper square commutes since $G$ is a functor, and the other three parts commute since $\eta$ is natural.
  If the red-colored maps are equivalent, then we can show that the upper horizontal map $(\eta_{\core})^\ast$ is an equivalence.
  If we apply this to the case $F$ is $\core$, then we obtain the desired result.
  This assumption follows from the next two propositions.
\end{proof}

The next proposition implies that $(\eta_{F})_{\ast}$ and $(G\eta_{\core})^{\ast}$ are equivalences.

\begin{proposition}[\cite{HLS23} Proposition 5.2] \label{HLS23.prop.5.2}
  Let $F : \Catst \to \An$ be an additive grouplike functor.
  Then the natural transformation
  \begin{align*}
    \eta_{F} : F \Rightarrow GF
  \end{align*}
  is an equivalence. 
\end{proposition}

The next proposition implies that $(\eta_{G\core})$ is an equivalence.

\begin{proposition}[\cite{HLS23} Proposition 5.3] \label{HLS23.prop.5.3}
  Let $F : \Catst \to \An$ be an additive functor.
  Then the two natural transformations
  \begin{align*}
    \eta_{GF} , G\eta_{F} : GF \Rightarrow GGF
  \end{align*}
  differ by an automorphism of the target.
  That is, the following diagram commutes
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$GF$}; 
    \node (tr) at (2,1.5) {$GGF$};
    \node (br) at (2,0) {$GGF.$}; 
    \draw (tl) -- node {$G\eta_{F}$} (tr); 
    \draw (tr) -- node {$\simeq$} (br); 
    \draw (tl) -- node[swap] {$\eta_{GF}$} (br);
  \end{tikzpicture}\] 
\end{proposition}


\section{The Cofinality Theorem}

The goal of this section is to prove the cofinality theorem.

\begin{theorem}[\cite{HLS23} Theorem 7.1: The Cofinality Theorem] \label{thrm.cofinality_theorem}
  Let $f : \C \subseteq \D$ be a dense inclusion of stable categories.
  Then it induces a fiber sequence
  \begin{align*}
    \K(\C) \to \K(\D) \to \K_0(\D)/\K_0(\C).
  \end{align*}
  In particular, maps of abelian groups
  \begin{align*}
    \K_i(\C) \to \K_i(\D)
  \end{align*}
  are isomorphisms for every $i \geq 1$, and there exists a short exact sequence 
  \begin{align*}
    0 \to \K_0(\C) \to \K_0(\D) \to \K_0(\D)/\K_0(\C) \to 0.
  \end{align*}
\end{theorem}

\Cref{thrm.cofinality_theorem} holds for a broader class of additive Karoubian functors (\cref{HLS23.thrm.7.7}).

\begin{definition}[\cite{HLS23} Definition 7.4] \label{HLS23.def.7.4}
  Let $f : X \to Y$ be a map of $\Einf$-monoids.
  We will say that $f$ is \textit{cofinal} if it satisfies the following conditions:
  \begin{enumerate}
    \item The map $\pi_0(f) : \pi_0(X) \to \pi_0(Y)$ is an inclusion.
    \item For every element $x$ in $\pi_0(X)$, there exists an element $x'$ in $\pi_0(X)$ such that $x+x'$ is in $\pi_0(Y)$.
  \end{enumerate}
  We will say that a cofinal map is \textit{dense} if it satisfies the following condition:
  \begin{enumerate}[resume]
    \setcounter{enumi}{2}
    \item The sequence of $\Einf$-monoids $0 \to \pi_0(X) \to \pi_0(Y) \to \pi_0(Y)/\pi_0(X) \to 0$ is exact. 
  \end{enumerate}
  Or equivalently, 
  \begin{itemize}
    \item[(3')] An element $y$ in $\pi_0(Y)$ belongs to $\pi_0(X)$ if there exists an element $x$ in $\pi_0(X)$ such that $x+y$ is in $\pi_0(X)$.
  \end{itemize}
\end{definition}

\begin{definition}[\cite{HLS23} Definition 7.6] \label{HLS23.def.7.6}
  Let $F : \Catst \to \An$ be an additive functor.
  We will say that $F$ is \textit{Karoubian} if it satisfies the following conditions:
  \begin{enumerate}
    \item The functor $F$ takes every dense inclusion between stable categories to a dense map of $\Einf$-monoids.
    \item The functor $F$ preserves every cartesian square in $\Catst$ whose vertical maps are dense.
  \end{enumerate}
\end{definition}

\begin{definition} \label{Ber.p171}
  Let $F : \Catst \to \An$ be an additive Karoubian functor.
  We will refer to the functor
  \begin{align*}
    F^{\grp}(-) := \Omega|FQ(-)| : \Catst \to \An
  \end{align*}
  as the \textit{group completion} of $F$.
\end{definition}

\begin{theorem}[\cite{HLS23} Theorem 7.7] \label{HLS23.thrm.7.7}
  Let $F : \Catst \to \An$ be an additive Karoubian functor.
  For every dense inclusion $\C \subseteq \D$ of stable categories, the canonical map of $\Einf$-monoids
  \begin{align*}
    F(\D)/F(\C) \to F^{\grp}(\D)/F^{\grp}(\C)
  \end{align*}
  is an equivalence.
  Hence maps of abelian groups
  \begin{align*}
    \pi_iF^{\grp}(\C) \to \pi_iF^{\grp}(\D)
  \end{align*}
  are isomorphisms for every $i \geq 1$, and there exists a short exact sequence 
  \begin{align*}
    0 \to \pi_0F^{\grp}(\C) \to \pi_0F^{\grp}(\D) \to \pi_0F^{\grp}(\D)/\pi_0F^{\grp}(\C) \to 0.
  \end{align*}
\end{theorem}

\begin{corollary}[\cite{HLS23} Corollary 7.8] \label{HLS23.cor.7.8}
  Let $F : \Catst \to \An$ be an additive Karoubian functor.
  Then the group completion 
  \begin{align*}
    F^{\grp} : \Catst \to \An
  \end{align*}
  of $F$ is also additive Karoubian.
  Moreover if $F^{\grp}$ is Verdier-localizing, then the functor
  \begin{align*}
    F^{\grp} \circ (-)^{\natural} : \Catst \to \An
  \end{align*}
  is Karoubi-localizing.
\end{corollary}

\begin{example} \label{Ber.rem.5.50}
  The core functor $\core : \Catst \to \An$ is (additive) Karoubian.

  (1):
  Let $\C \hookrightarrow \D$ be a dense inclusion of stable categories.
  Then the map $\core f : \core\C \to \core\D$ is cofinal.
  Let $d$ be an element in $\pi_0(\core\D)$, and let $c$ be an element in $\pi_0(\core\C)$ such that $c+d$ is in $\pi_0(\core\C)$.
  Then we have an equivalence $d \simeq \fib(c \oplus d \to c)$.
  The element $d$ is in $\pi_0(\core\C)$ since $\C$ is closed under fibers.
  That is, $\core f$ is dense.

  (2):
  The core functor preserves limits, since it is a right adjoint functor.
\end{example}

\begin{example} \label{eg.group_completion_of_core}
  The group completion 
  \begin{align*}
    (\core)^{\grp} : \Catst \to \An
  \end{align*}
  of $\core : \Catst \to \An$ is equivalent to the algebraic K-theory $\K : \Catst \to \An$.
\end{example}

\begin{example} \label{Ber.cor.5.52}
  By \cref{HLS23.cor.7.8,eg.group_completion_of_core}, the algebraic K-theory $\K : \Catst \to \An$ is additive Karoubian.
  By \cref{thrm.localization_theorem}, $\K$ is Verdier-localizing.
  Then the functor 
  \begin{align*}
    \K \circ (-)^{\natural} : \Catst \to \An
  \end{align*}
  is Karoubi-localizing.
\end{example}


\section{The Non-connective K-Theory}

\subsection{The Connective K-Theory}

\begin{remark}
  As stated in \cref{Ber.cor.5.52}, the functor 
  \begin{align*}
    \K \circ (-)^{\natural} : \Catst \to \An
  \end{align*}
  is Karoubi-localizing.
  In particular, it is an additive functor.
  Moreover, by \cref{Ber.rem.3.65}, it is also grouplike.
  Consequently, it lifts to a functor 
  \begin{align*}
    \K \circ (-)^{\natural} : \Catst \to \Grp(\An).
  \end{align*}
  Since there exists an equivalence $\Grp(\An) \simeq \Sp_{\geq 0}$, we obtain a functor 
  \begin{align*}
    \K \circ (-)^{\natural} : \Catst \to \Sp_{\geq 0}.
  \end{align*}
\end{remark}

\begin{definition}
  We will refer to the functor constructed above
  \begin{align*}
    \K_{\geq 0} := \K \circ (-)^{\natural} : \Catst \to \Sp_{\geq 0}
  \end{align*}
  as the \textit{connective K-theory}.
\end{definition}

\begin{remark}
  For every Karoubi square 
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$\C'$}; 
    \node (tr) at (1.5,1.5) {$\C$};
    \node (bl) at (0,0) {$\D'$}; 
    \node (br) at (1.5,0) {$\D$}; 
    % horizontal lines
    \draw (tl) -- node {} (tr); 
    \draw (bl) -- node[swap] {} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tr) -- node {} (br);
    % pullback symbol (\lrcorner) in the lower right corner of (tl)
    \node at (tl.south east) {$\lrcorner$}; 
  \end{tikzpicture}\]
  in $\Catst$, we obtain a cartesian square
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$\K_{\geq 0}(\C')$}; 
    \node (tr) at (2,1.5) {$\K_{\geq 0}(\C)$};
    \node (bl) at (0,0) {$\K_{\geq 0}(\D')$}; 
    \node (br) at (2,0) {$\K_{\geq 0}(\D)$}; 
    % horizontal lines
    \draw (tl) -- node {} (tr); 
    \draw (bl) -- node[swap] {} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tr) -- node {} (br); 
    % pullback symbol (\lrcorner) in the lower right corner of (tl)
    \node at (tl.south east) {$\lrcorner$};
  \end{tikzpicture}\]
  in $\Sp_{\geq 0}$.
  However, in general, it is not a cartesian square in $\Sp$ since the inclusion $\Sp_{\geq 0} \subseteq \Sp$ is not left exact.
\end{remark}

\begin{remark}
  For every Karoubi sequence $\C \to \D \to \E$, we obtain a long exact sequence
  \begin{align*}
    \cdots \to \K_1(\E) \to \K_0(\C) \to \K_0(\D) \to \K_0(\E).
  \end{align*}
  However, in general, the last map $\K_0(\D) \to \K_0(\E)$ is not surjective.
  To extend this sequence, we need to define the non-connective K-theory.
\end{remark}

\subsection{The Non-connective K-Theory}

In this section, let $\kappa$ be an uncountable regular cardinal.

\begin{remark}
  Let $\C$ be a stable category.
  By \cref{CDH23.cor.A.3.8}, the sequence
  \begin{align*}
    \C \to \Ind_{\omega}(\C)^{\kappa} \to (\Ind_{\omega}(\C)^{\kappa}/\C)^{\natural}
  \end{align*}
  in $\Catst$ is a Karoubi sequence.
\end{remark}

\begin{definition}
  Let $\C$ be a stable category.
  Then we will refer to
  \begin{align*}
    \Calk(\C) 
    := (\Ind_{\omega}(\C)^{\kappa}/\C)^{\natural}
  \end{align*}
  as the \textit{Calkin category}.
\end{definition}

\begin{definition}[\cite{BGT13} Definition 9.6]
  Let $\C$ be a stable category.
  We will refer to the category
  \begin{align*}
    \bbK(\C) 
    := \colim_{n} \Omega^n \K_{\geq 0}(\Calk(\C)),
  \end{align*}
  where taking the colimit in $\Sp$, as the \textit{non-connective K-theory spectrum}.

  The construction $\C \mapsto \bbK(\C)$ determines a functor 
  \begin{align*}
    \bbK : \Catst \to \Sp.
  \end{align*}
  We will refer to it as the \textit{non-connective K-theory}.
\end{definition}

\newpage
\appendix


\section{Proofs in \Cref{sec.localization_properties}}

\begin{newproof}[\Cref{Ber.rem.3.53}] \label{proof_of_Ber.rem.3.53}
  We show that every Verdier square is a cocartesian diagram in $\Catst$.
  Consider the following Verdier square.
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$\D$}; 
    \node (tr) at (1.5,1.5) {$\D'$};
    \node (bl) at (0,0) {$\E$}; 
    \node (br) at (1.5,0) {$\E',$}; 
    % horizontal lines
    \draw (tl) -- node {} (tr); 
    \draw (bl) -- node[swap] {} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tr) -- node {} (br); 
    % pullback symbol (\lrcorner) in the lower right corner of (tl)
    \node at (tl.south east) {$\lrcorner$};
  \end{tikzpicture}\]
  Since the vertical maps are Verdier projections, we can extend it to the following diagram.
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$\C$};
    \node (tm) at (1.5,1.5) {$\D$}; 
    \node (tr) at (3,1.5) {$\D'$};
    \node (bl) at (0,0) {$0$}; 
    \node (bm) at (1.5,0) {$\E$};
    \node (br) at (3,0) {$\E'$}; 
    % horizontal lines
    \draw (tl) -- node {} (tm); 
    \draw (tm) -- node {} (tr); 
    \draw (bl) -- node[swap] {} (bm); 
    \draw (bm) -- node[swap] {} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tm) -- node {} (bm);
    \draw (tr) -- node {} (br);
    % pullback symbol (\lrcorner) in the lower right corner of 
    % \node at (tl.south east) {$\lrcorner$};
    \node at (tm.south east) {$\lrcorner$};
    % pushout symbol (\ulcorner) in the upper left corner of
    % \node at (bm.north west) {$\ulcorner$};
    % \node at (br.north west) {$\ulcorner$};
  \end{tikzpicture}\]
  By definition, the left and outer squares are bicartesian squares.
  Then the right square is also a bicartesian square.
\end{newproof}

\begin{newproof}[\Cref{CDH23.prop.1.5.5}] \label{proof_of_CDH23.prop.1.5.5}
  (1) $\Rightarrow$ (2) is obvious.

  (2) $\Rightarrow$ (1): 
  Consider the following Verdier square.
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$\D$}; 
    \node (tr) at (1.5,1.5) {$\D'$};
    \node (bl) at (0,0) {$\E$}; 
    \node (br) at (1.5,0) {$\E',$}; 
    % horizontal lines
    \draw (tl) -- node {} (tr); 
    \draw (bl) -- node[swap] {} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tr) -- node {} (br); 
    % pullback symbol (\lrcorner) in the lower right corner of (tl)
    \node at (tl.south east) {$\lrcorner$};
  \end{tikzpicture}\]
  Then we can extend it to the following diagram.
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$\C$};
    \node (tm) at (1.5,1.5) {$\D$}; 
    \node (tr) at (3,1.5) {$\D'$};
    \node (bl) at (0,0) {$0$}; 
    \node (bm) at (1.5,0) {$\E$};
    \node (br) at (3,0) {$\E'$}; 
    % horizontal lines
    \draw (tl) -- node {} (tm); 
    \draw (tm) -- node {} (tr); 
    \draw (bl) -- node[swap] {} (bm); 
    \draw (bm) -- node[swap] {} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tm) -- node {} (bm);
    \draw (tr) -- node {} (br);
    % pullback symbol (\lrcorner) in the lower right corner of 
    \node at (tl.south east) {$\lrcorner$};
    \node at (tm.south east) {$\lrcorner$};
    % pushout symbol (\ulcorner) in the upper left corner of
    % \node at (bm.north west) {$\ulcorner$};
    % \node at (br.north west) {$\ulcorner$};
  \end{tikzpicture}\]
  By definition, the left, right, and outer squares are cartesian squares.
  Thus sequences $\C \to \D \to \E$ and $\C \to \D' \to E'$ are Verdier in $\Catst$.
  By assumption, sequences $F(\C) \to F(\D) \to F(\E)$ and $F(\C) \to F(\D') \to F(\E')$ are fiber sequences in $\E$.
  Then the left and outer squares in the following diagram are cartesian squares. 
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$F(\C)$};
    \node (tm) at (2,1.5) {$F(\D)$}; 
    \node (tr) at (4,1.5) {$F(\D')$};
    \node (bl) at (0,0) {$\ast$}; 
    \node (bm) at (2,0) {$F(\E)$};
    \node (br) at (4,0) {$F(\E')$}; 
    % horizontal lines
    \draw (tl) -- node {} (tm); 
    \draw (tm) -- node {} (tr); 
    \draw (bl) -- node[swap] {} (bm); 
    \draw (bm) -- node[swap] {} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tm) -- node {} (bm);
    \draw (tr) -- node {} (br);
    % pullback symbol (\lrcorner) in the lower right corner of 
    \node at (tl.south east) {$\lrcorner$};
    \node at (tm.south east) {$\lrcorner$};
    % pushout symbol (\ulcorner) in the upper left corner of
    % \node at (bm.north west) {$\ulcorner$};
    % \node at (br.north west) {$\ulcorner$};
  \end{tikzpicture}\]
  Then the right square is also a cartesian square.
\end{newproof}

\begin{newproof}[\Cref{HLS23.obs.2.2}] \label{proof_of_HLS23.obs.2.2}
  We show that every Verdier-localizing functor preserves finite products.
  Let $\E$ be a category with finite limits, and let $F : \Catst \to \E$ be a Verdier-localizing functor.
  The following diagram is a cartesian square in $\Catst$.
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$\C \times \D$}; 
    \node (tr) at (1.5,1.5) {$\D$};
    \node (bl) at (0,0) {$\C$}; 
    \node (br) at (1.5,0) {$0.$}; 
    % horizontal lines
    \draw (tl) -- node {} (tr); 
    \draw (bl) -- node[swap] {} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tr) -- node {} (br); 
    % pullback symbol (\lrcorner) in the lower right corner of (tl)
    \node at (tl.south east) {$\lrcorner$};
  \end{tikzpicture}\]
  Applying the functor $F$, we obtain the following cartesian square in $\E$.
  \[\begin{tikzpicture}[auto,->] 
    \node (tl) at (0,1.5) {$F(\C \times \D)$}; 
    \node (tr) at (2,1.5) {$F(\D)$};
    \node (bl) at (0,0) {$F(\C)$}; 
    \node (br) at (2,0) {$\ast.$}; 
    % horizontal lines
    \draw (tl) -- node {} (tr); 
    \draw (bl) -- node[swap] {} (br); 
    % vertical lines
    \draw (tl) -- node[swap] {} (bl);
    \draw (tr) -- node {} (br); 
    % pullback symbol (\lrcorner) in the lower right corner of (tl)
    \node at (tl.south east) {$\lrcorner$};
  \end{tikzpicture}\]
  This implies that 
  \begin{align*}
    F(\C \times \D) \simeq F(\C) \times F(\D).
  \end{align*}
\end{newproof}


\section{Proofs in \Cref{sec.algebraic_k_theory}}

To prove \cref{HLS23.prop.3.2}, we need some preliminaries.

\begin{notation}
  For every $n \geq 0$, we let $\J_n$ denote the full subcategory of $\TwAr[n]$ spanned by the images of objects $(i \leq j)$ satisfying $j \leq i+1$.
\end{notation}

\begin{lemma} \label{Ber.lem.4.28}
  Let $\C$ be a category with finite limits, and let $F : \TwAr[n] \to \E$ be a functor.
  The following conditions are equivalent:
  \begin{enumerate}
    \item The functor $F$ belongs to $Q_n(\C)$.
    \item The functor $F$ is the right Kan extension of its restriction to $\J_n$ along the inclusion $\J_n \subseteq \TwAr[n]$.
  \end{enumerate}
\end{lemma}

\begin{proof}
  The map 
  \begin{align*}
    e_i : [1] \to [n] : 0 \mapsto i \text{ and } 1 \mapsto i+1
  \end{align*}
  in $\Delta$ induces an equivalence of categories 
  \begin{align*}
    \J_n 
    \simeq \J_1 \coprod_{\J_0} \J_1 \cdots \coprod_{\J_0} \J_1 
    \simeq \TwAr[1] \coprod_{\TwAr[0]} \TwAr[1] \cdots \coprod_{\TwAr[0]} \TwAr[1]
  \end{align*}
  in $\Catlex$.
  Then the right Kan extension along the inclusion $\J_n \subseteq \TwAr[n]$ factors through $n(n-1)/2$-times the right Kan extension along the inclusion $\J_i \subseteq \TwAr[i]$ for every $n \geq 2$.
  The right Kan extension along the inclusion $\J_2 \subseteq \TwAr[2]$ correspondences the operation of taking the pullback.
  Then the equivalence of conditions follows from that a functor $F$ belong to $Q_n(\C)$ if and only if each square is a cartesian square.
\end{proof}

The next corollary follows from \cref{Ber.lem.4.28} immediately.

\begin{corollary} \label{Ber.cor.4.31}
  Let $\C$ be a category with finite limits.
  Then the restriction of $\Fun(\TwAr[n],\C)$ along the inclusion $\J_n \subseteq \TwAr[n]$ induces an equivalence of categories
  \begin{align*}
    Q_n(\C) \to \Fun(\J_n,\C).
  \end{align*}
\end{corollary}

\begin{newproof}[\Cref{HLS23.prop.3.2}] \label{proof_of_HLS23.prop.3.2}
  (TBA)
\end{newproof}

\printbibliography


\end{document}

% \subsection{The Algebraic K-Theory Spectrum}

% We can define the algebraic K-theory spectrum $\K_{\geq 0} : \Catst \to \Sp_{\geq 0}$ from the algebraic K-theory $\K : \Catst \to \An$.

% \begin{definition}
%   \Cref{HLS23.cor.4.2} implies that the algebraic K-theory $\K : \Catst \to \An$ lifts to the functor 
%   \begin{align*}
%     \K : \Catst \to \Grp(\An).
%   \end{align*}
%   Since there exists the equivalence $\Grp(\An) \simeq \Sp_{\geq 0}$, we obtain a functor 
%   \begin{align*}
%     \K_{\geq 0} : \Catst \to \Sp_{\geq 0}.
%   \end{align*}
%   We will refer to it as the \textit{algebraic K-theory spectrum}.
% \end{definition}

% \begin{remark}
%   There exists the equivalence $\Omega^\infty : \Sp_{\geq 0} \rightleftarrows \Grp(\An) : \Sigma^\infty$.
%   We can recover the algebraic K-theory from the algebraic K-theory spectrum as 
%   \begin{align*}
%     \K \simeq \Omega^\infty \K_{\geq 0} : \Catst \to \Sp_{\geq 0} \simeq \Grp(\An) \to \An,
%   \end{align*}
%   since $\Sigma^\infty$ is fully faithful.
% \end{remark}
